---
title: "Alcohol vs Seat choice"
author: "Brennen Long"
date: "2/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
 Our Goal is to answer this question:

Is there a difference between the alcohol consumed between the row you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This boxplot shows us that heavy drinkers tend to stay more to the back.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

People who sit towards the back drink 3x more alcohol than the people who prefer to sit in the middle or the back.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The P value is small enough that it is very unlikely that the total alcohol consumption in all three seat slots is the same.

```{r}
plot(TukeyHSD(model1))
```

The Turkey plot shows that people in the back drink a significant amount more than people in the front as the data shows the people in the middle. The middle shows no data other than average alcohol consumption.

## Conclusions

The evidence shows that people that consume alcohol tend to sit near the back of classrooms.

